Storing messages with multipartite neural cliques

### 2014-06-27 Articles/article.tex
...
théorie
écriture forumle

@@

>>>>

	\begin{figure}
		\includegraphics[width=8.5cm]{comp_erreurs_a2l512c4er1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
	\end{figure}

@@

	\newpage

	Formula for errors insted of erasures :

	$P(n_{gc} = (c - c_e - 1) + \gamma + x) = {c_e \choose x} d^x (1-d)^{ce-x}$

	$P(n_{ge} = (c - c_e) + \gamma + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$

	$P(n_{abe} = \gamma + x) = {c - 1 \choose x} d^x (1-d)^{c-1-x}$

	$P(n_{be} = x) = P(n_{bc} = x) = {c - 1 \choose x} d^x (1-d)^{c- 1 -x}$

	\begin{align*}
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	\end{align*}

	$P_{err} = 1 - P_{retrieve}$
